\documentclass[11pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{float}
\usepackage{lmodern,amsmath,amssymb,amstext,amsfonts,mathrsfs,graphicx,caption, subcaption}
\usepackage[width=14cm]{geometry}
\usepackage[colorlinks,pdfpagelabels,pdfstartview = FitV,bookmarksnumbered = true, bookmarksopenlevel=section, linkcolor = black, urlcolor = black ,hypertexnames = false,citecolor = black,pdfpagelabels=false]{hyperref}
\usepackage{tablefootnote}
%\usepackage{rotating}
\usepackage{textcmds, enumitem}
\usepackage{sidecap} %, indentfirst
\usepackage[labelfont={bf,sf},font={small},labelsep=space]{caption}
\usepackage{chngcntr} % 			** Damit die Bilder Tabellen und Gleichungen 
\counterwithin{figure}{section}	%	** alle nach Kapiteln nummeriert sind.
\counterwithin{table}{section}%		**
\counterwithin{equation}{section}%	**	

\begin{document}
	\section*{Acknowledgements}
	
	I would like to express my sincere gratitude to all those who have contributed to the completion of this master's thesis.
	
	First and foremost, I am deeply indebted to Professor Matthias Kaschube for delivering an inspiring lecture that ignited my interest in the field of theoretical neuroscience. Your guidance and encouragement have been invaluable throughout this journey.
	
	I extend my thanks to Sigrid Trägenap for her invaluable assistance in brainstorming ideas and collaborating on project updates. Your insights and dedication have significantly enriched this research.
	
	To the entire group, I am immensely grateful for creating a supportive environment that fostered growth and learning during the thesis period. Your constructive feedback and meticulous proofreading have significantly enhanced the quality of my work.
	
	I am indebted to the Frankfurt Institute for Advanced Studies for providing me with a conducive working environment, enabling me to focus and excel in my research endeavors. 
	
	Moreover, I extend my sincere appreciation to the Deutschlandstipendium for the financial support that has made pursuing my academic goals possible.
	
	To my cherished family and friends, your steadfast support and encouragement have been my guiding light on this journey. Your unwavering belief in me has provided continuous strength and motivation. 
	
	A heartfelt acknowledgment also goes to Tolga Tel for his meticulous proofreading, insightful feedback, and unwavering emotional support. Your presence beside me has been a consistent source of strength and inspiration.
	
	Lastly, I am deeply grateful to every individual who has played a part in this journey, contributing to its success in their unique way. Thank you all for being by my side and making this achievement possible.
	
	\section*{Supplementary material}
	
	Python code to reproduce the key results of this master's thesis is publicly available on GitHub under \url{https://github.com/rzhou-space/ffrec_alignment_hypothesis_masterthesis}
	
\end{document}